Appendix B: Code for analysis comparing to historical data

### 2019-04-11 appendix/appendixB.Rmd
ramlegacy data no longer available
from ramlegacy.org.  Use cached version instead

```{r}
if(!file.exists("ramlegacy.zip")){
download.file(paste0(
  "https://depts.washington.edu/ramlegac/wordpress/databaseVersions/",
  "RLSADB_v3.0_(assessment_data_only)_excel.zip"),
  "ramlegacy.zip")
}
```

```{r}
path <- unzip("ramlegacy.zip")
sheets <- readxl::excel_sheets(path)
ram <- lapply(sheets, readxl::read_excel, path = path)
names(ram) <- sheets

>>>>

```{r}
path <- "../data/appendixB/ramlegacy_v3.0.xlsx"
sheets <- readxl::excel_sheets(path)
ram <- lapply(sheets, readxl::read_excel, path = path)
names(ram) <- sheets
